Annotation exploration for `r params$scpca_project_id`

### 2024-09-24 analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

The aim is to explore the annotations and label transfers for all of the samples in `r params$scpca_project_id`.

@@

set.seed(params$seed)
```

@@

The fetal full reference (Cao et al.) provides three levels of annotations:

- `fetal_full_predicted.organ` is one of the 15 organs used for building the reference. 
We were nicely surprised that, for many of the samples, most of the cells from the Wilms tumor cohort mapped to fetal kidney cells.

- `fetal_full_predicted.annotation.l1` holds predicted cell type annotation

- `fetal_full_predicted.annotation.l2` holds the combination of the predicted organ and predicted cell type annotation

>>>>

The aim is to explore the annotations and label transfers for all of the samples in SCPCP000006.

@@

@@

This notebook looks at the `fetal_full_predicted.organ` annotation from this reference.
